Upgrades to the SINQ Cold Neutron Source

### 2015-09-16 paper.tex
revisions

Two variance reduction methods were used in conjunction to perform the simulations in a reasonable amount of time.  First, mesh-based weight windows were generated based on the response of a point detector located inside the AMOR neutron guide.  The point detector was positioned 75 cm from the guide entrance, giving it an approximately a two degree view towards the cold source.  The generated weight windows serve to increase the number of neutrons in regions that make large contributions to the point detector, which in this case is the cold source. In order to not bias the simulation, the weight windows cause neutrons entering the cold source to be split into many neutrons with a lower individual statistical weight.

@@

The guide reflectivity model implemented in MCNP is identical to that used in McStas \cite{mcnp_reflectivity}.  The reflectivity curve for the current AMOR guide is shown in Figure \ref{SINQ_reflectivity} and the reflectivity equation and parameter values shown in Eq. \ref{eq:ref} \cite{mcstas}.  The values shown are the same for all the straight guides in the SINQ hall \cite{SINQ_guide_values}.  The dimensions of the guides are slightly different, however, as can be seen from their horizontal cross sections in Figure \ref{geom}.

@@

With all of the variance reduction and approximations implemented, each case took about one hour to run on a 144-core configuration on a computer cluster at PSI.  The spectra from all the cases are shown in the upper plot of Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.  The figure of merit was chosen to be the total current exiting the AMOR guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall \cite{intruments_wavelength}.  The parameters were varied in slope-width-depth order, with slope being the fastest varied parameter. Figure \ref{parametric_REH} has labeled, colored blocks in the lower plot to show which parameters are constant for that block.  Slope and opening width have the most effect on the exit current at large hole depths.

>>>>

Two variance reduction methods were used in conjunction to perform the simulations in a reasonable amount of time.  First, mesh-based weight windows were generated based on the response of a point detector located inside the AMOR/SANS-I neutron guide.  The point detector was positioned 75 cm from the guide entrance, giving it an approximately a two degree view towards the cold source.  The generated weight windows serve to increase the number of neutrons in regions that make large contributions to the point detector, which in this case is the cold source. In order to not bias the simulation, the weight windows cause neutrons entering the cold source to be split into many neutrons with a lower individual statistical weight.

@@

The guide reflectivity model implemented in MCNP is identical to that used in McStas \cite{mcnp_reflectivity}.  The reflectivity curve for the current AMOR/SANS-I guide is shown in Figure \ref{SINQ_reflectivity} and the reflectivity equation and parameter values shown in Eq. \ref{eq:ref} \cite{mcstas}.  The values shown are the same for all the straight guides in the SINQ hall \cite{SINQ_guide_values}.  The dimensions of the guides are slightly different, however, as can be seen from their horizontal cross sections in Figure \ref{geom}.

@@

With all of the variance reduction and approximations implemented, each case took about one hour to run on a 144-core configuration on a computer cluster at PSI.  The spectra from all the cases are shown in the upper plot of Figure \ref{parametric_REH}, and their figures of merit are shown in the lower plot.  The figure of merit was chosen to be the total current exiting the AMOR/SANS-I guide from 3 to 6 \AA{} -- the wavelength band which is useful for most of the instruments in the guide hall \cite{intruments_wavelength}.  The parameters were varied in slope-width-depth order, with slope being the fastest varied parameter. Figure \ref{parametric_REH} has labeled, colored blocks in the lower plot to show which parameters are constant for that block.  Slope and opening width have the most effect on the exit current at large hole depths.
